Manuscript_1

### 2024-04-03 Manuscript_1.Rmd
Edit Figure 4A

# Plot
chrom_AI = ggplot(AI_ATAC,
                  aes(Sample.n, 
                      Reads, 
                      fill = interaction(Sample.n, Base)), 
                  alpha = Base) +
  geom_bar(stat = "identity",
           position = "dodge",
           width = 0.5,
           colour = "black") +
  geom_text(aes(label = format(c(0.3,
                          "",
                          0.3,
                          "",
                          0.003,
                          "",
                          0.0000003,
                          "",
                          0.2,
                          ""),
                          scientific = TRUE),
                 y = Reads + 100),
            vjust = 0) +
  scale_fill_manual(aesthetics = "fill",
                    values = c("#D3D3D3",
                               "#B22222",
                               "#FF6347",
                               "#FFA07A",
                               "#b8627db2",
                               "#C0C0C0",
                               "#A52A2A",
                               "#FF0000",
                               "#FA8072",
                               "#cc6a70b2")) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 330)) +
  xlab("") +
  theme(axis.text = element_text(face = "bold", colour = "black"),
        axis.title.x = element_text(face = "bold", colour = "black"),
        legend.position = "none") 
#######################################################################

@@

chrom_AI = ggbarplot(AI_ATAC,
                     x = "Sample.n",
                     y = "Reads",
                     fill = "Allele",
                     position = position_dodge(0.7),
                     xlab = "",
                     ylab = "Reads",
                     title = "Read at SCARB2 promoter overlapping rs1465922 (SCARB2)",
                     label = format(c(0.3,
                          "",
                          0.3,
                          "",
                          0.003,
                          "",
                          0.0000003,
                          "",
                          0.2,
                          ""),
                          scientific = TRUE),
                     label.pos = "out",
                     lab.size = 3,
                     lab.vjust = 0.5,
                     lab.hjust = -0.5,
                     orientation = "horiz") +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1.0, face = "bold", size = 10),
        axis.text.y = element_text(face = "bold", size = 10),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.title.x = element_text(face = "bold", size = 10),
        legend.text = element_text(face = "bold", size = 10),
        legend.title = element_text(face = "bold", size = 10),
        plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#80A44F", "#427F96")) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 330))

>>>>

# Plot
chrom_AI = ggplot(AI_ATAC,
                  aes(Sample.n, 
                      Reads, 
                      fill = interaction(Sample.n, Base)), 
                  alpha = Base) +
  geom_bar(stat = "identity",
           position = "dodge",
           width = 0.5,
           colour = "black") +
  geom_text(aes(label = format(c(paste0("p = ",
                                        0.3),
                          "",
                          paste0("p = ",
                                 0.3),
                          "",
                          paste0("p = ",
                                 0.003),
                          "",
                          paste0("p = ",
                                 0.0000003),
                          "",
                          paste0("p = ",
                                 0.2),
                          ""),
                          scientific = TRUE),
                 y = Reads + 100),
            vjust = 0) +
  scale_fill_manual(aesthetics = "fill",
                    values = c("#D3D3D3",
                               "#B22222",
                               "#FF6347",
                               "#FFA07A",
                               "#b8627db2",
                               "#C0C0C0",
                               "#A52A2A",
                               "#FF0000",
                               "#FA8072",
                               "#cc6a70b2")) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 330)) +
  xlab("") +
  theme(axis.text = element_text(face = "bold", colour = "black"),
        axis.title.x = element_text(face = "bold", colour = "black"),
        legend.position = "none") 
#######################################################################

@@

chrom_AI = ggbarplot(AI_ATAC,
                     x = "Sample.n",
                     y = "Reads",
                     fill = "Allele",
                     position = position_dodge(0.7),
                     xlab = "",
                     ylab = "Reads",
                     title = "Read at SCARB2 promoter overlapping rs1465922 (SCARB2)",
                     label = format(c(paste0("p = ",
                                        0.3),
                          "",
                          paste0("p = ",
                                 0.3),
                          "",
                          paste0("p = ",
                                 0.003),
                          "",
                          paste0("p = ",
                                 0.0000003),
                          "",
                          paste0("p = ",
                                 0.2),
                          ""),
                          scientific = TRUE),
                     label.pos = "out",
                     lab.size = 3,
                     lab.vjust = 0.5,
                     lab.hjust = -0.5,
                     orientation = "horiz") +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1.0, face = "bold", size = 10),
        axis.text.y = element_text(face = "bold", size = 10),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.title.x = element_text(face = "bold", size = 10),
        legend.text = element_text(face = "bold", size = 10),
        legend.title = element_text(face = "bold", size = 10),
        plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#80A44F", "#427F96")) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 330))
